---
title: "Honours methods"
author: "Jess"
date: "2/21/2020"
output:
  pdf_document: default
  html_document: default
---

```{r, setup}
pacman::p_load(tidyverse,
               data.table,
               rscopus,
               wosr,
               rbace,
               lens2r,
               httr,
               XML,
               jsonlite,
               taxize,
               gtools)

devtools::install_github("jessicatytam/specieshindex", force = TRUE, build_vignettes = FALSE)
library(specieshindex)
```

**Functions**
0.1. create_query_string_T
  + creates a query string to make functions with a query cleaner
  + title only
0.2. create_query_string_TAK
  + creates a query string to make functions with a query cleaner
  + title + abstract + keywords
0.3. create_query_string_T_wos
  + creates a query string to make functions with a query cleaner
  + title only
0.4. create_query_string_TAK_wos
  + creates a query string to make functions with a query cleaner
  + title + abstract + keywords
0.5. create_query_string_T_base
  + creates a query string to make functions with a query cleaner
  + title only
0.6. create_query_string_TAK_base
  + creates a query string to make functions with a query cleaner
  + title + abstract + keywords
0.7. create_query_string_T_lens
  + creates a query string to make functions with a query cleaner
  + title only
0.8. create_query_string_TAK_lens
  + creates a query string to make functions with a query cleaner
  + title + abstract + keywords
1. CountSpT
  + counts the total number of search results on Scopus
  + title only
2. CountSpTAK
  + counts the total number of search results on Scopus
  + title + abstract + keywords
3. FetchSpT
  + fetches data from Scopus using genus and species name
  + title only
4. FetchSpTAK
  + fetches data from Scopus using genus and species name
  + title + abstract + keywords
5. TotalPub
  + counts the total number of publications
6. TotalCite
  + counts the total number of citations
7. TotalJournals
  + counts the total number of journals
8. TotalArt
  + counts the total number of articles
9. TotalRev
  + counts the total number of reviews
10. ARRatio
  + calculates article:review ratio
11. SpHindex
  + calculates h-index
12. YearsPublishing
  + calculates the number of years since the first publication
13. SpMindex
  + calculates m-index (h-index / total years)
14. Spi10
  + counts the publications with 10+ citations
15. SpH5
  + calculates h-index for the past 5 years
16. SpHAfterdate
  + calculates h-index with a given time frame
17. Allindices
  + shows a summary of the main indices



```{r, scopus query for title only searches}
create_query_string_T <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TITLE("', genus, ' ', species, '")'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TITLE("', genus, ' ', species, '" AND ', additionalkeywords, ')'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('TITLE("', genus, ' ', species, '" OR ', synonyms[1])
    if (length(synonyms)==1) {
      return(paste0(temp_string, ')'))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0(temp_string, ' OR ', synonyms[i])
      }
      return(paste0(temp_string, ')'))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('TITLE(("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')'))
  } 
}
```

```{r, scopus query for title, abstract, and keywords searches}
create_query_string_TAK <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TITLE-ABS-KEY("', genus, ' ', species, '")'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TITLE-ABS-KEY("', genus, ' ', species, '" AND ', additionalkeywords, ')'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('TITLE-ABS-KEY("', genus, ' ', species, '" OR ', synonyms[1])
    if (length(synonyms)==1) {
      return(paste0(temp_string, ')'))
    }
    else {
      for (i in 2:length(synonyms)){
         temp_string <- paste0(temp_string, ' OR ', synonyms[i])
      }
      return(paste0(temp_string, ')'))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('TITLE-ABS-KEY(("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')'))
  } 
}
```

```{r, wos query for title only searches}
create_query_string_T_wos <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TI = "', genus, ' ', species, '"'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TI = ("', genus, ' ', species, '" AND ', additionalkeywords, ')'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('TI = ("', genus, ' ', species, '" OR ', synonyms[1], ')')
    if (length(synonyms)==1) {
      return(paste0(temp_string))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0('TI = ("', genus, ' ', species, '" OR ', synonyms[i], ')')
      }
      return(paste0(temp_string))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('TI = (("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')'))
  } 
}
```

```{r, wos query for title only searches}
create_query_string_TAK_wos <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TI = "', genus, ' ', species,
                  '" OR AB = "', genus, ' ', species,
                  '" OR AK = "', genus, ' ', species, '"'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('TI = ("', genus, ' ', species, '" AND ', additionalkeywords, ')',
                  ' OR AB = ("', genus, ' ', species, '" AND ', additionalkeywords, ')',
                  ' OR AK = ("', genus, ' ', species, '" AND ', additionalkeywords, ')'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('TI = ("', genus, ' ', species, '" OR ', synonyms[1], ')',
                          ' OR AB = ("', genus, ' ', species, '" OR ', synonyms[1], ')',
                          ' OR AK = ("', genus, ' ', species, '" OR ', synonyms[1], ')')
    if (length(synonyms)==1) {
      return(paste0(temp_string))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0('TI = ("', genus, ' ', species, '" OR ', synonyms[i], ')',
                              ' OR AB = ("', genus, ' ', species, '" OR ', synonyms[i], ')',
                              ' OR AK = ("', genus, ' ', species, '" OR ', synonyms[i], ')')
      }
      return(paste0(temp_string))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('TI = (("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')',
                  ' OR AB = (("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')',
                  ' OR AK = (("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')'))
  } 
}
```

```{r, base query for title only searches}
create_query_string_T_base <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('dctitle:"', genus, ' ', species, '"'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('dctitle:("', genus, ' ', species, '" AND ', additionalkeywords, ')'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('dctitle:("', genus, ' ', species, '" OR ', synonyms[1])
    if (length(synonyms)==1) {
      return(paste0(temp_string, ')'))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0(temp_string, ' OR ', synonyms[i])
      }
      return(paste0(temp_string, ')'))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('dctitle:(("', genus, ' ', species, '" OR ', synonyms, ') AND ', additionalkeywords, ')'))
  } 
}
```

```{r, base query for title, abstract and keyword searches}
create_query_string_TAK_base <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('dctitle:"', genus, ' ', species, '"',
                  ' OR dcdescription:"', genus, ' ', species, '"',
                  ' OR dcsubject:"', genus, ' ', species, '"'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('dctitle:("', genus, ' ', species, '" AND ', additionalkeywords, ')',
                  ' OR dcdescription:("', genus, ' ', species, '" AND ', additionalkeywords, ')',
                  ' OR dcsubject:("', genus, ' ', species, '" AND ', additionalkeywords, ')'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('dctitle:("', genus, ' ', species, '" OR ', synonyms[1], ')',
                          ' OR dcdescription:("', genus, ' ', species, '" OR ', synonyms[1], ')',
                          ' OR dcsubject:("', genus, ' ', species, '" OR ', synonyms[1], ')')
    if (length(synonyms)==1) {
      return(paste0(temp_string))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0('dctitle:("', genus, ' ', species, '" OR ', synonyms[i], ')',
                              ' OR dcdescription:("', genus, ' ', species, '" OR ', synonyms[i], ')',
                              ' OR dcsubject:("', genus, ' ', species, '" OR ', synonyms[i], ')')
      }
      return(paste0(temp_string))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('dctitle:(("', genus, ' ', species, '"', ' OR ', synonyms, ') AND ', additionalkeywords, ')',
                  ' OR dcdescription:(("', genus, ' ', species, '"', ' OR ', synonyms, ') AND ', additionalkeywords, ')',
                  ' OR dcsubject:(("', genus, ' ', species, '"', ' OR ', synonyms, ') AND ', additionalkeywords, ')'))
  } 
}
```

```{r, lens query for title only searches}
create_query_string_T_lens <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\"",
					  "fields": ["title"]
				  }
			  }]
		  }
	  },
	  "size": 1000
  }'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\" AND ', additionalkeywords, '",
					  "fields": ["title"]
				  }
			  }]
		  }
	  },
	  "size": 1000
  }'))
  }
  if (missing(additionalkeywords)&!missing(synonyms)) {
    temp_string <- paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\" OR \\"', synonyms[1], '\\"",
					  "fields": ["title"]
				  }
			  }]
		  }
	  },
	  "size": 1000
  }')
    if (length(synonyms)==1) {
      return(paste0(temp_string))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\" OR \\"', synonyms[i], '\\"",
					  "fields": ["title"]
				  }
			  }]
		  }
	  },
	  "size": 1000
  }')
      }
      return(paste0(temp_string))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "(\\"', genus, ' ', species, '\\" OR \\"', synonyms, '\\") AND ', additionalkeywords, '",
					  "fields": ["title"]
				  }
			  }]
		  }
	  },
	  "size": 1000
  }'))
  } 
}
```

```{r, lens query for title, abstract, and keywords searches}
create_query_string_TAK_lens <- function(genus, species, synonyms, additionalkeywords){
  if (missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\"",
					  "fields": ["title", "abstract", "keyword"],
					  "default_operator": "or"
				  }
			  }]
		  }
	  },
	  "size": 1000
  }'))
  } 
  if (!missing(additionalkeywords) & missing(synonyms)) {
    return(paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\" AND ', additionalkeywords, '",
					  "fields": ["title", "abstract", "keyword"],
					"default_operator": "or"
				  }
			  }]
		  }
	  },
	  "size": 1000
  }'))
  }
  if (missing(additionalkeywords) & !missing(synonyms)) {
    temp_string <- paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\" OR \\"', synonyms[1], '\\"",
					  "fields": ["title", "abstract", "keyword"],
					"default_operator": "or"
				  }
			  }]
		  }
	  },
	  "size": 1000
  }')
    if (length(synonyms)==1) {
      return(paste0(temp_string))
    }
    else {
      for (i in 2:length(synonyms)){
        temp_string <- paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "\\"', genus, ' ', species, '\\" OR \\"', synonyms[i], '\\"",
					  "fields": ["title", "abstract", "keyword"],
					"default_operator": "or"
				  }
			  }]
		  }
	  },
	  "size": 1000
  }')
      }
      return(paste0(temp_string))
    }
  }
  if (!missing(additionalkeywords) & !missing(synonyms)) {
    return(paste0('{
    "query": {
		  "bool": {
			  "must": [{
				  "query_string": {
					  "query": "(\\"', genus, ' ', species, '\\" OR \\"', synonyms, '\\") AND ', additionalkeywords, '",
					  "fields": ["title", "abstract", "keyword"],
					"default_operator": "or"
				  }
			  }]
		  }
	  },
	  "size": 1000
  }'))
  } 
}
```

```{r, function to get result count from scopus title only}
#code from Fonti (modified)
CountSpT <- function(genus, species, synonyms, additionalkeywords, APIkey, datatype = "application/xml") {
  if (missing(APIkey)) {
    stop("You need to register for an API key on Scopus.") #stop running if API key missing
  }
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  ) 
  theURL <- httr::GET("http://api.elsevier.com/content/search/scopus",
                      query = list(apiKey = paste0(APIkey),
                                   query = create_query_string_T(genus, species, synonyms, additionalkeywords),
                                   httpAccept = "application/xml")) #format the URL to be sent to the API
  httr::stop_for_status(theURL) #pass any HTTP errors to the R console
  theData <- httr::content(theURL, as = "text") #extract the content of the response
  newData <- XML::xmlParse(theURL) #parse the data to extract values
  resultCount <- as.numeric(XML::xpathSApply(newData,"//opensearch:totalResults", XML::xmlValue)) #get the total number of search results for the string
  return(resultCount)
}
```

```{r, function to get result count from scopus title+abs+key}
#code from Fonti (modified)
CountSpTAK <- function(genus, species, synonyms, additionalkeywords, APIkey, datatype = "application/xml") {
  if (missing(APIkey)) {
    stop("You need to register for an API key on Scopus.") #stop running if API key missing
  }
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  ) 
  theURL <- httr::GET("http://api.elsevier.com/content/search/scopus",
                      query = list(apiKey = paste0(APIkey),
                                   query = create_query_string_TAK(genus, species, synonyms, additionalkeywords),
                                   httpAccept = "application/xml")) #format the URL to be sent to the API
  httr::stop_for_status(theURL) #pass any HTTP errors to the R console
  theData <- httr::content(theURL, as = "text") #extract the content of the response
  newData <- XML::xmlParse(theURL) #parse the data to extract values
  resultCount <- as.numeric(XML::xpathSApply(newData,"//opensearch:totalResults", XML::xmlValue)) #get the total number of search results for the string
  return(resultCount)
}
```

```{r, fetch from scopus using title only, message=FALSE}
#this function downloads citation data from scopus
FetchSpT <- function(genus, species, synonyms, additionalkeywords, language = 0, APIkey) {
  count <- CountSpT(genus, species, synonyms, additionalkeywords, APIkey) #check the number of records
  print(paste(count, "records found."))
  if (count < 1) {
    noCitations <- data.frame(citations = 0)
    return(noCitations)
  }
  if (language == 1) {
    lang <- read.csv(file = "data/languages.csv", header = T)[-c(1)]
    datalist <- data.frame()
    for (j in 1:length(lang$language)) {
      theURL <- httr::GET("http://api.elsevier.com/content/search/scopus",
                          query = list(apiKey = paste0(APIkey),
                                       query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords),
                                                      " AND LANGUAGE(", lang$language[j], ")"),
                                       httpAccept = "application/xml")) #format the URL to be sent to the API
      httr::stop_for_status(theURL) #pass any HTTP errors to the R console
      theData <- httr::content(theURL, as = "text") #extract the content of the response
      newData <- XML::xmlParse(theURL) #parse the data to extract values
      resultCount <- as.numeric(XML::xpathSApply(newData,"//opensearch:totalResults", XML::xmlValue)) #get the total number of search results for the string
      if (resultCount > 0) {
        #search begins
        search2020 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 2019 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search2020df <- rscopus::entries_to_citation_df(search2020$entries)
        searchloopdf = data.frame()
        for (i in 2019:1990) {
          searchloop <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR = ", i, " AND LANGUAGE(", lang$language[j], ")")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          searchlooplist <- rscopus::entries_to_citation_df(searchloop$entries)
          searchloopdf <- dplyr::bind_rows(searchloopdf, searchlooplist)
          }
        search1985 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1984 AND PUBYEAR < 1990 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search1985df <- rscopus::entries_to_citation_df(search1985$entries)
        search1980 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1979 AND PUBYEAR < 1985 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search1980df <- rscopus::entries_to_citation_df(search1980$entries)
        search1975 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1974 AND PUBYEAR < 1980 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search1975df <- rscopus::entries_to_citation_df(search1975$entries)
        search1970 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1969 AND PUBYEAR < 1975 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)  
        search1970df <- rscopus::entries_to_citation_df(search1970$entries)
        search_old <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR < 1970 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search_olddf <- rscopus::entries_to_citation_df(search_old$entries)
        langlist <- dplyr::bind_rows(search2020df, searchloopdf, search1985df, search1980df, search1975df, search1970df, search_olddf)
        langlist$language <- lang$language[j]
        #search ends
        datalist <- dplyr::bind_rows(datalist, langlist)
      }
      }
    datalist <- datalist[!is.na(datalist$title), ] #remove NA papers
  } else {
    #loop if count is under 5000
    if (count <= 5000) {
      step_size <- 1000 #the number of records to retrieve in each loop
      start_record <- 0
      datalist = data.frame()
      looprepeat <- ceiling(count/step_size)-1 #the number of loop times, rounded up to the nearest integer
      #loop starts
      for (i in 0:looprepeat) { 
        print(paste("starting iteration: ", i, " Note: iteration size is ", step_size, " records, which runs of 200 records inside each iteration."))
        print(paste("Fetching records now."))
        search <- rscopus::scopus_search(query = create_query_string_T(genus, species, synonyms, additionalkeywords),
                                         api_key = paste0(APIkey),
                                         verbose = TRUE,
                                         max_count = step_size,
                                         start = step_size*i,
                                         wait_time = 3)
        start_record <- as.numeric(summary(search)[1,1]) #move the pointer of starting record for each iteration to a new value
        searchdf <- rscopus::entries_to_citation_df(search$entries)
        list <- data.frame(searchdf)
        datalist <- rbind(datalist, list)
        #loop ends
        }} else {
          #search begins
          search2020 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 2019")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          search2020df <- rscopus::entries_to_citation_df(search2020$entries)
          searchloopdf = data.frame()
          for (i in 2019:1990) {
            searchloop <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR = ", i)),
                                                 api_key = paste0(APIkey),
                                                 verbose = TRUE,
                                                 wait_time = 3)
            searchlooplist <- rscopus::entries_to_citation_df(searchloop$entries)
            searchloopdf <- rbind(searchloopdf, searchlooplist)
            }
          search1985 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1984 AND PUBYEAR < 1990")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          search1985df <- rscopus::entries_to_citation_df(search1985$entries)
          search1980 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1979 AND PUBYEAR < 1985")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          search1980df <- rscopus::entries_to_citation_df(search1980$entries)
          search1975 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1974 AND PUBYEAR < 1980")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)  
          search1975df <- rscopus::entries_to_citation_df(search1975$entries)
          search1970 <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1969 AND PUBYEAR < 1975")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)  
          search1970df <- rscopus::entries_to_citation_df(search1970$entries)
          search_old <- rscopus::scopus_search(query = paste0(create_query_string_T(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR < 1970")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)  
          search_olddf <- rscopus::entries_to_citation_df(search_old$entries)
          datalist <- rbind(search2020df, searchloopdf, search1985df, search1980df, search1975df, search1970df, search_olddf)
          #search ends  
        }
    }
  returned <- dim(datalist)[1]
  print(paste(returned, "records retrived in total."))
  #showing final list of records
  retrieved <- dim(datalist)[1] #check the number
  print(paste(retrieved, "unique records successfully fetched."))
  return(datalist)
}
```

```{r, fetch from scopus using title+abs+key, message=FALSE}
#this function downloads citation data from scopus
FetchSpTAK <- function(genus, species, synonyms, additionalkeywords, language = 0, APIkey) {
  count <- CountSpTAK(genus, species, synonyms, additionalkeywords, APIkey) #check the number of records
  print(paste(count, "records found."))
  if (count < 1) {
    noCitations <- data.frame(citations = 0)
    return(noCitations)
  }
  if (language == 1) {
    lang <- read.csv(file = "data/languages.csv", header = T)[-c(1)]
    datalist <- data.frame()
    for (j in 1:length(lang$language)) {
      theURL <- httr::GET("http://api.elsevier.com/content/search/scopus",
                          query = list(apiKey = paste0(APIkey),
                                       query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords),
                                                      " AND LANGUAGE(", lang$language[j], ")"),
                                       httpAccept = "application/xml")) #format the URL to be sent to the API
      httr::stop_for_status(theURL) #pass any HTTP errors to the R console
      theData <- httr::content(theURL, as = "text") #extract the content of the response
      newData <- XML::xmlParse(theURL) #parse the data to extract values
      resultCount <- as.numeric(XML::xpathSApply(newData,"//opensearch:totalResults", XML::xmlValue)) #get the total number of search results for the string
      if (resultCount > 0) {
        #search begins
        search2020 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 2019 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search2020df <- rscopus::entries_to_citation_df(search2020$entries)
        searchloopdf = data.frame()
        for (i in 2019:1990) {
          searchloop <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR = ", i, " AND LANGUAGE(", lang$language[j], ")")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          searchlooplist <- rscopus::entries_to_citation_df(searchloop$entries)
          searchloopdf <- dplyr::bind_rows(searchloopdf, searchlooplist)
          }
        search1985 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1984 AND PUBYEAR < 1990 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search1985df <- rscopus::entries_to_citation_df(search1985$entries)
        search1980 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1979 AND PUBYEAR < 1985 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search1980df <- rscopus::entries_to_citation_df(search1980$entries)
        search1975 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1974 AND PUBYEAR < 1980 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search1975df <- rscopus::entries_to_citation_df(search1975$entries)
        search1970 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1969 AND PUBYEAR < 1975 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)  
        search1970df <- rscopus::entries_to_citation_df(search1970$entries)
        search_old <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR < 1970 AND LANGUAGE(", lang$language[j], ")")),
                                             api_key = paste0(APIkey),
                                             verbose = TRUE,
                                             wait_time = 3)
        search_olddf <- rscopus::entries_to_citation_df(search_old$entries)
        langlist <- dplyr::bind_rows(search2020df, searchloopdf, search1985df, search1980df, search1975df, search1970df, search_olddf)
        langlist$language <- lang$language[j]
        #search ends
        datalist <- dplyr::bind_rows(datalist, langlist)
      }
      }
    datalist <- datalist[!is.na(datalist$title), ] #remove NA papers
  } else {
    #loop if count is under 5000
    if (count <= 5000) {
      step_size <- 1000 #the number of records to retrieve in each loop
      start_record <- 0
      datalist = data.frame()
      looprepeat <- ceiling(count/step_size)-1 #the number of loop times, rounded up to the nearest integer
      #loop starts
      for (i in 0:looprepeat) { 
        print(paste("starting iteration: ", i, " Note: iteration size is ", step_size, " records, which runs of 200 records inside each iteration."))
        print(paste("Fetching records now."))
        search <- rscopus::scopus_search(query = create_query_string_TAK(genus, species, synonyms, additionalkeywords),
                                         api_key = paste0(APIkey),
                                         verbose = TRUE,
                                         max_count = step_size,
                                         start = step_size*i,
                                         wait_time = 3)
        start_record <- as.numeric(summary(search)[1,1]) #move the pointer of starting record for each iteration to a new value
        searchdf <- rscopus::entries_to_citation_df(search$entries)
        list <- data.frame(searchdf)
        datalist <- rbind(datalist, list)
        #loop ends
        }} else {
          #search begins
          search2020 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 2019")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          search2020df <- rscopus::entries_to_citation_df(search2020$entries)
          searchloopdf = data.frame()
          for (i in 2019:1990) {
            searchloop <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR = ", i)),
                                                 api_key = paste0(APIkey),
                                                 verbose = TRUE,
                                                 wait_time = 3)
            searchlooplist <- rscopus::entries_to_citation_df(searchloop$entries)
            searchloopdf <- rbind(searchloopdf, searchlooplist)
            }
          search1985 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1984 AND PUBYEAR < 1990")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          search1985df <- rscopus::entries_to_citation_df(search1985$entries)
          search1980 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1979 AND PUBYEAR < 1985")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)
          search1980df <- rscopus::entries_to_citation_df(search1980$entries)
          search1975 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1974 AND PUBYEAR < 1980")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)  
          search1975df <- rscopus::entries_to_citation_df(search1975$entries)
          search1970 <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR > 1969 AND PUBYEAR < 1975")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)  
          search1970df <- rscopus::entries_to_citation_df(search1970$entries)
          search_old <- rscopus::scopus_search(query = paste0(create_query_string_TAK(genus, species, synonyms, additionalkeywords), paste0(" AND PUBYEAR < 1970")),
                                               api_key = paste0(APIkey),
                                               verbose = TRUE,
                                               wait_time = 3)  
          search_olddf <- rscopus::entries_to_citation_df(search_old$entries)
          datalist <- rbind(search2020df, searchloopdf, search1985df, search1980df, search1975df, search1970df, search_olddf)
          #search ends  
        }
    }
  returned <- dim(datalist)[1]
  print(paste(returned, "records retrived in total."))
  #showing final list of records
  retrieved <- dim(datalist)[1] #check the number
  print(paste(retrieved, "unique records successfully fetched."))
  return(datalist)
}
```

```{r, function to get result count from scopus title only}
CountSpT_wos <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  count <- wosr::query_wos(query = create_query_string_T_wos(genus, species, synonyms, additionalkeywords),
                           sid = sid) 
  return(count)
}
```

```{r, function to get result count from scopus title+abs+key}
CountSpTAK_wos <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  count <- wosr::query_wos(query = create_query_string_TAK_wos(genus, species, synonyms, additionalkeywords),
                           sid = sid) 
  return(count)
}
```

```{r, fetch from wos using title, message=FALSE}
#this function downloads citation data from wos
FetchSpT_wos <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  query <- wosr::pull_wos(query = create_query_string_T_wos(genus, species, synonyms, additionalkeywords),
                          sid = sid) 
  results <- data.table::rbindlist(query, fill = TRUE)
  results <- data.table::setDT(results)[, lapply(.SD, function(x) x[!is.na(x)][1L]), by = ut]
  #renaming columns
  names(results)[names(results) == "tot_cites"] <- "citations"
  names(results)[names(results) == "doc_type"] <- "description"
  names(results)[names(results) == "date"] <- "cover_date"
  return(results)
}
```

```{r, fetch from wos using title, message=FALSE}
#this function downloads citation data from wos
FetchSpTAK_wos <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  query <- wosr::pull_wos(query = create_query_string_TAK_wos(genus, species, synonyms, additionalkeywords),
                          sid = sid) 
  results <- data.table::rbindlist(query, fill = TRUE)
  results <- data.table::setDT(results)[, lapply(.SD, function(x) x[!is.na(x)][1L]), by = ut]
  #renaming columns
  names(results)[names(results) == "tot_cites"] <- "citations"
  names(results)[names(results) == "doc_type"] <- "description"
  names(results)[names(results) == "date"] <- "cover_date"
  return(results)
}
```

```{r}
CountSpT_base <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  theURL <- httr::GET("https://api.base-search.net/cgi-bin/BaseHttpSearchInterface.fcgi",
                      query = list(query = create_query_string_T_base(genus, species, synonyms, additionalkeywords),
                                   httpAccept = "application/xml")) #format the URL to be sent to the API
  httr::stop_for_status(theURL) #pass any HTTP errors to the R console
  theData <- httr::content(theURL, as = "text") #extract the content of the response
  newData <- XML::xmlParse(theURL) #parse the data to extract values
  resultCount <- as.numeric(XML::xpathSApply(newData,"//opensearch:totalResults", XML::xmlValue)) #get the total number of search results for the string
  return(resultCount)
}
```

```{r, fetch from base using title, message=FALSE}
#this function downloads citation data from base
FetchSpT_base <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  #loop
  results <- data.frame()
  start <- 1
  for (i in start:(start+124)) { #number of loops to be determined by the count of the documents
    print(paste("Fetching documents", start, "to", start+124))
    query <- rbace::bs_search(query = create_query_string_T_base(genus, species, synonyms, additionalkeywords),
                              hits = 125,
                              offset = start-1) 
    query <- data.table::rbindlist(query, fill = TRUE)
    results <- dplyr::bind_rows(results, query)
    start <- start+125
  }
  #renaming columns
  #names(results)[names(results) == "tot_cites"] <- "citations"
  #names(results)[names(results) == "doc_type"] <- "description"
  #names(results)[names(results) == "date"] <- "cover_date"
  return(results)
}
```

```{r, fetch from base using title only, message=FALSE}
#this function downloads citation data from base
FetchSpTAK_base <- function(genus, species, synonyms, additionalkeywords) {
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  query <- rbace::bs_search(query = create_query_string_TAK_base(genus, species, synonyms, additionalkeywords),
                            hits = 125) 
  results <- data.table::rbindlist(query, fill = TRUE)
  #renaming columns
  #names(results)[names(results) == "tot_cites"] <- "citations"
  #names(results)[names(results) == "doc_type"] <- "description"
  #names(results)[names(results) == "date"] <- "cover_date"
  return(results)
}
```

```{r, function to get result count from lens title only}
CountSpT_lens <- function(genus, species, synonyms, additionalkeywords, token) {
  if (missing(token)) {
    stop("You need to register for a token on Lens.") #stop running if token missing
  }
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  ) 
  theURL <- httr::POST(url = "https://api.lens.org/scholarly/search",
                       add_headers(.headers = c("Authorization" = token,
                                                "Content-Type" = "application/json")),
                       body = create_query_string_T_lens(genus, species, synonyms, additionalkeywords))
  lens_content <- jsonlite::fromJSON(rawToChar(theURL$content))
  if (!is.null(lens_content$total)) {
    resultCount <- as.numeric(lens_content$total)
  } else {
    resultCount <- 0
  }
  return(resultCount)
}
```

```{r, function to get result count from lens title, abstract, and keywords only}
CountSpTAK_lens <- function(genus, species, synonyms, additionalkeywords, token) {
  if (missing(token)) {
    stop("You need to register for a token on Lens.") #stop running if token missing
  }
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  ) 
  theURL <- httr::POST(url = "https://api.lens.org/scholarly/search",
                       add_headers(.headers = c("Authorization" = token,
                                                "Content-Type" = "application/json")),
                       body = create_query_string_TAK_lens(genus, species, synonyms, additionalkeywords))
  lens_content <- jsonlite::fromJSON(rawToChar(theURL$content))
  resultCount <- as.numeric(lens_content$total)
  return(resultCount)
}
```

```{r, fetch from lens using title, message=FALSE}
#this function downloads citation data from lens
FetchSpT_lens <- function(genus, species, synonyms, additionalkeywords, token) {
  if (missing(token)) {
    stop("You need to register for a token on Lens.") #stop running if API key missing
  }
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  )
  results <- lens2r::get_scholarly_df(query = create_query_string_T_lens(genus, species, synonyms, additionalkeywords),
                                      token = token)
  #renaming columns
  names(results)[names(results) == "scholarly_citations_count"] <- "citations"
  names(results)[names(results) == "source.title"] <- "journal"
  names(results)[names(results) == "publication_type"] <- "description"
  names(results)[names(results) == "date_published"] <- "cover_date"
  #replacing NA with 0
  for (i in 1:nrow(results)) {
    if (is.na(results$citations[i])) {
      results$citations[i] <- 0
    }
  }
  #clean cover_date
  results$cover_date <- substr(results$cover_date, 1, 10)
  return(results)
}
```

```{r, fetch from lens using title+abs+key, message=FALSE}
#this function downloads citation data from lens
FetchSpTAK_lens <- function(genus, species, synonyms, additionalkeywords, token) {
  if (missing(token)) {
    stop("You need to register for a token on Lens.") #stop running if API key missing
  }
  findname <- taxize::gnr_resolve(sci = c(genus, species)) #check if the species exist
  dplyr::case_when(
    findname$submitted_name %in% findname$matched_name ~ print(paste("Species found on the Encyclopedia of Life."))
  ) 
  results <- lens2r::get_scholarly_df(query = create_query_string_TAK_lens(genus, species, synonyms, additionalkeywords),
                                      token = token)
  #renaming columns
  names(results)[names(results) == "scholarly_citations_count"] <- "citations"
  names(results)[names(results) == "source.title"] <- "journal"
  names(results)[names(results) == "publication_type"] <- "description"
  names(results)[names(results) == "date_published"] <- "cover_date"
  #replacing NA with 0
  for (i in 1:nrow(results)) {
    if (is.na(results$citations[i])) {
      results$citations[i] <- 0
    }
  }
  #clean cover_date
  results$cover_date <- substr(results$cover_date, 1, 10)
  return(results)
}
```

```{r, total publications}
#this function calculates the total number of publications
TotalPub <- function(data) {
  total <- nrow(data) #counts the number of publications by summing the records
  return(total)
}
```

```{r, total citations}
#this function calculates the total number of citations
TotalCite <- function(data) {
  data$citations <- as.numeric(data$citations) #changes the class to numerical for calculation
  total <- sum(data$citations) #sums all of the citations
  return(total)
}
```

```{r, total journals}
#this function calculates the total number of journals
TotalJournals <- function(data) {
  filter <- unique(data$journal) #filters data to pick out each journal
  total <- length(filter) #counts the number of journals
  return(total)
}
```

```{r, total articles}
#this function calculates the total number of articles
TotalArt <- function(data) {
  Article <- sum(data$description == "Article") #calculates the number of articles
  return(Article)
}
```

```{r, total reviews}
#this function calculates the total number of reviews
TotalRev <- function(data) {
  Review <- sum(data$description == "Review") #calculates the number of reviews
  return(Review)
}
```

```{r, article:review ratio}
#this function calculates the ratio of articles:rerviews
ARRatio <- function(data) {
  Article <- sum(data$description == "Article") #calculates the number of articles
  Review <- sum(data$description == "Review") #calculates the number of reviews
  ArticleRatio <- signif(Article/(Article+Review)*100, digits = 4) #percentage of articles, rounded to 4 sf
  ReviewRatio <- signif(Review/(Article+Review)*100, digits = 4) #percentage of reviews, rounded to 4 sf
  Ratio <- paste(ArticleRatio, ":", ReviewRatio) #prints ratio
  return(Ratio)
}
```

```{r, species h-index}
#this function calculates the h-index
SpHindex <- function(data) {
  data$citations <- as.numeric(data$citations) #change class from factor to numeric
  sorteddf <- sort(data$citations, decreasing = TRUE) #sort in descending order
  Hindex <- 0   #computes h-index
  for(i in 1:length(sorteddf)) {
    if (sorteddf[i] > Hindex) {
      Hindex <- Hindex + 1
    }
  }
  return(Hindex)
}
```

```{r, years of publication}
#this function canculates the number of years since the first publication
YearsPublishing <- function(data) {
  data$year <- as.numeric(substr(data$cover_date, 1, 4))
  as.numeric(substr(Sys.Date(), 1, 4)) - min(data$year) #time since first publication in years
  years_publishing <- as.numeric(substr(Sys.Date(), 1, 4)) - min(data$year) #time since first publication in years
  return(years_publishing)
}
```

```{r, m-index}
#this function calculates the m-index
#it does not requires the calculation of the h-index beforehand
SpMindex <- function(data) {
  data$citations <- as.numeric(data$citations) #change class from factor to numeric
  sorteddf <- sort(data$citations, decreasing = TRUE) #sort in descending order
  Hindex <- 0   #computes h-index
  for(i in 1:length(sorteddf)) {
    if (sorteddf[i] > Hindex) {
      Hindex <- Hindex + 1
    }
  }
  data$year <- as.numeric(substr(data$cover_date, 1, 4))
  years_publishing <- as.numeric(substr(Sys.Date(), 1, 4)) - min(data$year) #time since first publication in years
  Mindex <- round(Hindex/years_publishing, digits = 3) #round to 3 decimal places
  return(Mindex)
}
```

```{r, i10 index}
#this function calculates the i10 index
#i10 index counts all of the publications with 10+ citations
Spi10 <- function(data) {
  data$citations <- as.numeric(data$citations) #changes class from factor to numeric
  sorteddf <- sort(data$citations, decreasing = TRUE) #sorts in descending order
  i10 <- sum(sorteddf>=10) #counts the publications with 10 or more citations
  return(i10)
}
```

```{r, h5 index}
#this function calculates the h-index of the past 5 years
SpH5 <- function(data) { #last 5 years from the current date
  current_date <- as.numeric(substr(Sys.Date(), 1, 4)) #current year
  #The easiest thing to do is to convert it into POSIXlt and subtract 5 from the years slot.
  d <- as.POSIXlt(Sys.Date())
  d$year <- d$year-5
  if (d < 1) { #the index is 0 if there are no records form the past 5 years
    return(as.numeric("0"))
  }
  as.Date(d)
  h5 <- SpHAfterdate(data, d)
  return(h5) #calls HAfterdate function
}
```

```{r, h-index with a given date}
#this function calculates the h-index using a given date up till the newest record
SpHAfterdate <- function(data, date) {
  data$cover_date <- as.Date(data$cover_date, format = "%Y-%m-%d") #change format of the date from factor to date
  subsetdata <- dplyr::filter(data, cover_date > as.Date(date))
  if (dplyr::count(subsetdata) < 1) { #the index is 0 if there are no records in this time frame
    return(as.numeric("0"))
  }
  HAfterdate <- SpHindex(subsetdata) #calls Hindex function
  return(HAfterdate)
}
```

```{r, shows main indices}
#this function returns a summary of all of the indices
Allindices <- function(data, genus, species) {
  if (all.equal(0, data$citations) == TRUE) {
    zeroIndex <- data.frame(genus_species = paste0(genus, "_", species),
                            species = paste0(species),
                            genus = paste0(genus),
                            publications = 0, citations = 0, journals = 0, articles = 0, reviews = 0, years_publishing = NA,
                            h = 0, m = 0, i10 = 0, h5 = 0)
    return(zeroIndex)
  } else {
    combine <- data.frame(paste0(genus, "_", species), paste0(species), paste0(genus), TotalPub(data), TotalCite(data),
                        TotalJournals(data),TotalArt(data),TotalRev(data), YearsPublishing(data),
                        SpHindex(data), SpMindex(data), Spi10(data), SpH5(data))
    combine[is.na(combine)] <- 0 #replace NA values with 0
    colnames(combine) <- c("genus_species", "species", "genus","publications", "citations", "journals", "articles", "reviews",
                           "years_publishing", "h", "m", "i10", "h5")
    return(combine)
  }
  cat("\n", genus, species, "\n",
      TotalPub(data), "publications", "\n",
      TotalCite(data), "citations", "\n",
      TotalJournals(data), "journals", "\n",
      TotalArt(data), "articles", "\n",
      TotalRev(data), "reviews", "\n",
      YearsPublishing(data), "years of publishing", "\n",
      "h:", SpHindex(data), "\n",
      "m:", SpMindex(data), "\n",
      "i10:", Spi10(data), "\n",
      "h5:", SpH5(data))
}
```


**Tests**

```{r, woylie}
#test done on 10 july
CountSpT("Bettongia", "penicillata", myAPI) #45
CountSpTAK("Bettongia", "penicillata", myAPI) #113
FetchSpTAK("Bettongia", "penicillata", myAPI) #no duplicates

TotalPub(Woylie) #113
TotalCite(Woylie) #1897
TotalJournals(Woylie) #55
TotalArt(Woylie) #110
TotalRev(Woylie) #3
ARRatio(Woylie) #97.35 : 2.655

YearsPublishing(Woylie) #43
SpHindex(Woylie) #26
SpMindex(Woylie) #0.6046512
Spi10(Woylie) #54
SpH5(Woylie) #8
SpHAfterdate(Woylie, "2000-01-01") #20

B_penicillata <- Allindices(Woylie, genus = "Bettongia", species = "penicillata")
```

```{r, quokka}
#test done on 10 july
CountSpTAK("Setonix", "brachyurus", myAPI) #242
Quokka <- FetchSpTAK("Setonix", "brachyurus", myAPI) #no duplicates

TotalPub(Quokka) #242
TotalCite(Quokka) #3423
TotalJournals(Quokka) #107
TotalArt(Quokka) #237
TotalRev(Quokka) #5
ARRatio(Quokka) #97.93 : 2.066

YearsPublishing(Quokka) #66
SpHindex(Quokka) #29
SpMindex(Quokka) #0.4393939
Spi10(Quokka) #121
SpH5(Quokka) #3
SpHAfterdate(Quokka, "2000-01-01") #17

S_brachyurus <- Allindices(Quokka, genus = "Setonix", species = "brachyurus")
```

```{r, platypus}
#test done on 10 july
CountSpTAK #321
Platypus <- FetchSpTAK("Ornithorhynchus", "anatinus", myAPI) #no duplicates

TotalPub(Platypus) #321
TotalCite(Platypus) #6363
TotalJournals(Platypus) #153
TotalArt(Platypus) #308
TotalRev(Platypus) #13
ARRatio(Platypus) #95.95 : 4.05

YearsPublishing(Platypus) #67
SpHindex(Platypus) #41
SpMindex(Platypus) #0.6119403
Spi10(Platypus) #177
SpH5(Platypus) #7
SpHAfterdate(Platypus, "2000-01-01") #32

O_anatinus <- Allindices(Platypus, genus = "Ornithorhynchus", species = "anatinus")
```

```{r, koala}
#test done on 10 july
CountSpTAK("Phascolarctos", "cinereus", myAPI) #777
FetchSpT("Phascolarctos", "cinereus", additionalkeywords = "(consrv* OR protect* OR reintrod* OR restor*)", "442b9048417ef20cf680a0ae26ee4d86") #3
FetchSpT("Phascolarctos", "cinereus", APIkey = "442b9048417ef20cf680a0ae26ee4d86") #446; 3 duplicates

CountSpT("Phascolarctos", "cinereus", additionalkeywords = "(consrv* OR protect* OR reintrod* OR restor*)", "442b9048417ef20cf680a0ae26ee4d86") #3
CountSpT("Phascolarctos", "cinereus", additionalkeywords = "(popul* W/5 ecolog*)", "442b9048417ef20cf680a0ae26ee4d86") #0
CountSpT("Phascolarctos", "cinereus", additionalkeywords = "(breed* OR reprod* OR fertil* OR fecund*)", "442b9048417ef20cf680a0ae26ee4d86") #21
CountSpT("Phascolarctos", "cinereus", additionalkeywords = "(popul* AND NOT popular)", "442b9048417ef20cf680a0ae26ee4d86") #49
CountSpT("Phascolarctos", "cinereus", additionalkeywords = "NOT (phylog* OR taxonom*)", "442b9048417ef20cf680a0ae26ee4d86") #447
CountSpT("Phascolarctos", "cinereus", APIkey = "442b9048417ef20cf680a0ae26ee4d86") #449

CountSpTAK("Phascolarctos", "cinereus", additionalkeywords = "(consrv* OR protect* OR reintrod* OR restor*)", "442b9048417ef20cf680a0ae26ee4d86") #70
CountSpTAK("Phascolarctos", "cinereus", additionalkeywords = "(popul* W/5 ecolog*)", "442b9048417ef20cf680a0ae26ee4d86") #11
CountSpTAK("Phascolarctos", "cinereus", additionalkeywords = "(breed* OR reprod* OR fertil* OR fecund*)", "442b9048417ef20cf680a0ae26ee4d86") #143
CountSpTAK("Phascolarctos", "cinereus", additionalkeywords = "(popul* AND NOT popular)", "442b9048417ef20cf680a0ae26ee4d86") #322
CountSpTAK("Phascolarctos", "cinereus", additionalkeywords = "NOT (phylog* OR taxonom*)", "442b9048417ef20cf680a0ae26ee4d86") #758
CountSpTAK("Phascolarctos", "cinereus", APIkey = "442b9048417ef20cf680a0ae26ee4d86") #826

TotalPub(Koala) #773
TotalCite(Koala) #14291
TotalJournals(Koala) #227
TotalArt(Koala) #744
TotalRev(Koala) #29
ARRatio(Koala) #96.25 : 3.752

YearsPublishing(Koala) #139
SpHindex(Koala) #53
SpMindex(Koala) #0.381295
Spi10(Koala) #427
SpH5(Koala) #15
SpHAfterdate(Koala, "2000-01-01") #44

P_cinereus <- Allindices(Koala, genus = "Phascolarctos", species = "cinereus")
```

```{r, combining the datasets}
Combinedata <- rbind(B_penicillata, S_brachyurus, O_anatinus, P_cinereus)

plot(Combinedata$publications)
plot(Combinedata$citations)
plot(Combinedata$journals)
plot(Combinedata$articles)
plot(Combinedata$reviews)
plot(Combinedata$years_publishing)
plot(Combinedata$h)
plot(Combinedata$m) #this is quite interesting
plot(Combinedata$i10)
plot(Combinedata$h5) #woylie has a pretty high index here
```

```{r, manual tests}
#test with dummy data
dummy1 <- data.frame("citations" = c(12, 5, 0, 21, 3, 4, 9, 17, 1, 10,
                                     10, 1, 0, 16, 26, 24, 15, 34, 31, 29),
                     "cover_date" = c(2000, 2015, 1986, 1994, 1972, 2002, 2006, 2019, 2016, 2006,
                                      1997, 1989, 2007, 2010, 2013, 2020, 2017, 1994, 1999, 2016))
SpHindex(dummy1) #10
YearsPublishing(dummy1) #48
SpMindex(dummy1) #0.2083333
Spi10(dummy1) #12

```



```{r, testing}
sid <- auth(username = NULL, password = NULL)

test <- pull_wos(query = 'TS = "Bettongia penicillata"',
                 sid = sid)
query_wos(query = 'TI = "Bettongia penicillata"',
          sid = sid) #42 matching records
CountSpT_wos(genus = "Bettongia", species = "penicillata")
test_df <- as.data.frame(test$publication)

test_df2 <- rbindlist(test, fill = TRUE)
test_df2_collapse <- setDT(test_df2)[, lapply(.SD, function(x) x[!is.na(x)][1L]), by = ut]

CountSpT_wos(genus = "Osphranter", species = "rufus") #3
CountSpT_wos(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"') #115
CountSpT_wos(genus = "Osphranter", species = "rufus", additionalkeywords = "conserv*") #0
CountSpT_wos(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"', additionalkeywords = "conserv*") #1

CountSpTAK_wos(genus = "Osphranter", species = "rufus") #8
CountSpTAK_wos(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"') #199
CountSpTAK_wos(genus = "Osphranter", species = "rufus", additionalkeywords = "conserv*") #1
CountSpTAK_wos(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"', additionalkeywords = "conserv*") #11

woylie_wosT <- FetchSpT_wos(genus = "Bettongia", species = "penicillata")
Allindices(woylie_wosT, genus = "Bettongia", species = "penicillata")



base_test <- bs_search(query = "dctitle:Bettongia penicillata", hits = 125) #108
base_test <- bs_search(query = 'dctitle:"Bettongia penicillata"', hits = 125) #99

kangaroo1_base <- FetchSpTAK_base(genus = "Osphranter", species = "rufus") #9
kangaroo2_base <- FetchSpT_base(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"') #125
kangaroo3_base <- FetchSpTAK_base(genus = "Osphranter", species = "rufus", additionalkeywords = "conserv*") #4
kangaroo4_base <- FetchSpTAK_base(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"', additionalkeywords = "conserv*") #22

CountSpT_base(genus = "Osphranter", species = "rufus", synonyms = '"Macropus rufus"')



base <- httr::GET("https://api.base-search.net/cgi-bin/BaseHttpSearchInterface.fcgi",
                      query = list(query = 'dctitle:("Osphranter rufus" OR "Macropus rufus")',
                                   httpAccept = "application/json")) #format the URL to be sent to the API
theData <- httr::content(base, as = "text") #access denied
rawToChar(base$content) #access denied


lens <- GET("https://api.lens.org/scholarly/search?token=KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb&query=title(%22Macropus%20rufus%22)")
rawToChar(lens$content)
lens_content <- fromJSON(rawToChar(lens$content))
length(lens_content$data$lens_id)
names(lens_content)
lens_content$total

"https://api.lens.org/scholarly/search?token=KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb&query=title(%22Macropus%20rufus%22)"
"https://api.lens.org/scholarly/search?token=KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb&query=title(%22Macropus%20rufus%22%20OR%20%22Osphranter%20rufus%22)"
"https://api.lens.org/scholarly/search?token=KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb&query=title(%22Bettongia%20penicillata%22)"
"https://api.lens.org/scholarly/search?token=KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb&query=title(%22Bettongia%20penicillata%22%20AND%20conserv*)"

theURL <- httr::GET("http://api.elsevier.com/content/search/scopus",
                      query = list(apiKey = "442b9048417ef20cf680a0ae26ee4d86",
                                   query = 'TITLE("Bettongia penicillata")',
                                   httpAccept = "application/xml")) #format the URL to be sent to the API
theData <- httr::content(theURL, as = "text") #extract the content of the response
newData <- XML::xmlParse(theURL)
resultCount <- as.numeric(XML::xpathSApply(newData,"//opensearch:totalResults", XML::xmlValue))


url <- 'https://api.lens.org/scholarly/search'
headers <- c('Authorization' = token, 'Content-Type' = 'application/json')
httr::POST(url = url, add_headers(.headers=headers), body = query)

dat <- POST(url = "https://api.lens.org/scholarly/search",
            add_headers(.headers = c("Authorization" = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb",
                                     "Content-Type" = "application/json")),
            body = test_query(genus = "Macropus", species = "rufus", additionalkeywords = "conserv*")) #http 400
rawdata <- jsonlite::fromJSON(rawToChar(dat$content))
rawdata$total


CountSpT_lens(genus = "Osphranter", species = "rufus", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #4
CountSpT_lens(genus = "Osphranter", species = "rufus", synonyms = "Macropus rufus", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #146
CountSpT_lens(genus = "Macropus", species = "rufus", additionalkeywords = "conserv*", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #2
CountSpT_lens(genus = "Osphranter", species = "rufus", synonyms = "Macropus rufus", additionalkeywords = "conserv*", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #2

CountSpTAK_lens(genus = "Osphranter", species = "rufus", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #10
CountSpTAK_lens(genus = "Macropus", species = "rufus", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #285
CountSpTAK_lens(genus = "Osphranter", species = "rufus", synonyms = "Macropus rufus", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #295
CountSpTAK_lens(genus = "Osphranter", species = "rufus", additionalkeywords = "conserv*", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #2
CountSpTAK_lens(genus = "Osphranter", species = "rufus", synonyms = "Macropus rufus", additionalkeywords = "conserv*", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb") #16

woylie_lens <- FetchSpTAK_lens(genus = "Bettongia", species = "penicillata", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb")
CountSpT_lens(genus = "Bettongia", species = "penicillata", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb")
CountSpTAK_lens(genus = "Bettongia", species = "penicillata", token = "KeQCynn4V050fJZwOmaPIzUpAe7Fn5Y4rOkk79jb2IgUTSBwBBOb")
Allindices(woylie_lens, genus = "Bettongia", species = "penicillata")

```

